Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-18 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:18	19:01:20	(Tue18.Aug)

The beamformer output $z[n]$ can now be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. We will refer to a set of weights as a window, but it is also commonly called a taper function. Conventional beamformers all have static weights, and by far the most common of these is the delay-and-sum (DAS) beamformer, which does exactly what the name implies.

>>>>

The beamformer output $z[n]$ can now be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. We will refer to a set of weights as a window, but it is also commonly called a taper function. Conventional beamformers all have static weights, and the reference here is the delay-and-sum (DAS) beamformer, or the backprojection algortithm. As the name implies it delays each pixel into focus, then applies a suitable window, and finally sums the data.
